The gobba functional programming language.\\WORK IN PROGRESS DRAFT

### 2020-01-19 paper/paper.tex
added completion with the latest ocamline library and ocaml-linenoise. quite broken

\begin{abstract}
\textbf{gobba} is a dynamically typed and purely functional interpreted
programming language. It is based on the Professor Gianluigi Ferrari and
Professor Francesca Levi's minicaml, an evaluation example to show students
attending the Programming 2 course at the University of Pisa how interpreters
work. It is an interpreted language heavily inspired from the OCaml, Haskell and
Scheme languages, with static (lexical scoping), a simple but effective module
system, eager and lazy evaluation and a didactical REPL that shows each AST
expression and each evaluation step.
\end{abstract}

\section{REPL and command line interface}
\subsection{Installation}

@@

>>>>

\begin{abstract}
\textbf{gobba} is a dynamically typed and purely functional interpreted
programming language. Based on Professors Gianluigi Ferrari and Francesca Levi's
minicaml interpreter example, the goal for gobba is to be a practical language with
built in support for scientific computing, solving some of the problems that
exist in other dynamically typed interpreted languages like python and Javascript. It is an
interpreted language heavily inspired from the OCaml, Haskell and Scheme
languages, with static (lexical scoping), a simple but effective module system,
eager and lazy evaluation and a didactical REPL that can show each AST
expression and each evaluation step.
\end{abstract}

\section{Installing gobba}

@@

\section{Interactive Command Line Interface}
If no filename is passed to \texttt{gobba} executable, the interactive shell
interface is launched. The REPL shell is built upon a simple library called
\texttt{ocamline} \cite{ocamline}, which itself relies on a library called
\texttt{ocaml-linenoise} \cite{linenoise} that provides \texttt{readline}
navigation and completion functionality without additional system
dependencies.
